---
title: "R Notebook"
output: html_notebook
---

## (a) Perform the following commands in R:
```{r}
set.seed(1)
x1 <- runif(100)
x2 <- 0.5*x1 + rnorm(100)/10
y <- 2 + 2*x1 + 0.3*x2 + rnorm(100)
```

### The last line corresponds to creating a linear model in which y is a function of x1 and x2. Write out the form of the linear model. What are the regression coefficients?
2, 0.3 and 2

## (b) What is the correlation between x1 and x2? Create a scatterplot displaying the relation- ship between the variables.
```{r}
cor(x1, x2)
plot(x1, x2)
```

## (c) Using the data, fit a least square regression to predict y using x1 and x2.
```{r}
model3 <- lm(y ~ x1 + x2)
summary(model3)
```

### What are the estimated parameters of ????0, ????1 and ????2? How do these relate to the true ??0, ??1 and ??
????0 is very close to the true ??0. However, the other 2 are not as close to their true values.

### Can you reject the null hypothesis H0 : ??1 = 0?
It can be rejected at a 5% and 1% significance level.

### How about the null hypothesis H0 : ??2 = 0?
It cannot be rejected.

## (d) Now fit a least squares regression to predict y using only x1.
```{r}
model4 <- lm(y ~ x1)
summary(model4)
```

### How does the estimated ????1 relate to the true ??1?
They are very similar. In fact ????1 is 0.0241 off from the true ??1 of 2.

### Can you reject the null hypothesis H0 : ??1 = 0?
Yes, as the p-value is very close to 0

## (e) Now fit a least squares regression to predict y using only x2.
```{r}
model5 <- lm(y ~ x2)
summary(model5)
```

### How does the estimated ????2 relate to the true ??2?
The value is very different from the true value of 0.3

### Can you reject the null hypothesis H0 : ??2 = 0?
Yes as the p-value is very close to 0

## (f) Provide an explanation on the results in parts (c)-(e).
There is multicollinearity in the data between x1 and x2. In doing multi- ple regression we see this effect where it is difficult to reject H0 : ??i = 0 (for one of the coefficients), while we see that with a single regression (with one variable), we can reject H0 : ??i = 0. This is caused by multicollinearity.